---
title: "Module 12"
output: html_document
date: "2025-04-14"
---

## Main Functions

1.dclean function
This function aims to elimate NA errors and faulty data. replacing the value to zero or an average of the data points.
Example Input: 5,7,NA, 2,NA,9
Example Output: 5,7,0,2,0,9
```{r }

dclean <- function(df, replace = 0){
  
  #example code
  
}



```


2. dformat function
   This allows the to change the data format to something R can read and calulate with. This includes the date format and numbers separated by commas. 
Example Input: 01/21/2000
Example Output: 2000-21-01
```{r }

dformat <- function(df, format = date){
  
  # example code
}



```


3.dclean.text function
This function allows the users to be able clear up any unnecessary punctuations, special character and unnecessary space.
Example Input: cash$@number
Example Output: cash number
```{r }

dclean.text <- function(x){

  
# Example Code    

  
}

```


4. dclean.names & d.rename 
These function allows allow for more control over the names of rows and columns in a dataframe. First function clean the existing names while the second rename the rows or columns the way you want to.

Example 1 input: total.NUm
Example 1 Output: total NUm
Example 2 input: toTal Numz
Example 2 Output: Total Number
```{r, }

dclean.names <- function(x){
  # Example code
}

d.rename <- function(x,y){
  # Example code
}

```

